### 2020-03-30 04-CCNA.tex
fino a sect4 e flat
update fino a sezione 4 inclusa e def di flat

\begin{example}
As some simple examples, consider the recursive process definitions $H \defeq \link{a}{b}.\link{a}{c}.H$ and $K \defeq \link{a}{b}.K + \link{a}{c}.K$: the former is some sort of forwarder that alternates between providing a link from $a$ to $b$ and to $c$ ; the latter is a nondeterministic forwarder that at each step can link $a$ to $b$ or to $c$. 
\end{example}

>>>>

\begin{example}
As some simple examples, consider the recursive process definitions $H \defeq \link{a}{b}.\link{a}{c}.H$ and $K \defeq \link{a}{b}.K + \link{a}{c}.K$: the former is some sort of forwarder that alternates between providing a link from $a$ to $b$ and to $c$; the latter is a nondeterministic forwarder that at each step can link $a$ to $b$ or to $c$. 
\end{example}
